Linked Data Notifications: a resource-centric communication protocol

### 2017-03-08 index.xh2latex.tex
fine-tuning; commenting some bib URLs

    p{.15\textwidth}

@@

    p{.07\textwidth}
    p{.07\textwidth}
    p{.09\textwidth}

@@

@@

                                                Webmention&

@@

                                                ResourceSync&

@@

\begin{thebibliography}{99}
  \bibitem{ref-1} Mansour, E., Sambra, A., Hawke, S., Zereba, M., Capadisli, S., Ghanem, A., Aboulnaga, A., Berners-Lee, T.: A Demonstration of the Solid Platform for Social Web Applications, WWW, Demo, 2016, \url{http://www2016.net/proceedings/companion/p223.pdf}
  \bibitem{ref-2} Tramp, S., Frischmuth, P., Ermilov, T., Shekarpour, S., Auer, S.: An Architecture of a Distributed Semantic Social Network, Semantic Web Journal, 2012
  \bibitem{ref-3} Arndt, N., Junghanns, K., Meissner, R., Frischmuth, F., Radtke, N., Frommhold, M., Martin, M.: Structured Feedback, WWW, LDOW, 2016, \url{http://events.linkeddata.org/ldow2016/papers/LDOW2016_paper_02.pdf}
  \bibitem{ref-4} Capadisli, S., Guy, A.: Linked Data Notifications, W3C Candidate Recommendation, 2016, \url{https://www.w3.org/TR/ldn/}
  \bibitem{ref-5} Parecki, A.: Webmention, W3C Proposed Recommendation, 2016,  \url{https://www.w3.org/TR/webmention/}
  \bibitem{ref-6} Langridge, S., Hickson, I.: Pingback 1.0, 2002,  \url{http://www.hixie.ch/specs/pingback/pingback}
  \bibitem{ref-7} Klyne, G., Groth, P.: PROV-AQ: Provenance Access and Query,  W3C Note, 2013, \url{http://www.w3.org/TR/prov-aq/}
  \bibitem{ref-8} Haslhofer, B., Popitsch, N.: DSNotify – Detecting and Fixing Broken Links in Linked Data Sets, WWW, 2010, \url{http://eprints.cs.univie.ac.at/81/1/2010\_WWW\_DSNotify.pdf}
  \bibitem{ref-9} Passant, A., Mendes, P.N.: sparqlPuSH: Proactive notification of data updates in RDF stores using PubSubHubbub, SFSW, CEUR Workshop Proceedings, Vol. 699, 2010, \url{http://ceur-ws.org/Vol-699/Paper6.pdf}
  \bibitem{ref-10} Klein, M., Van de Sompel, H., Warner, S., Klyne, G., Haslhofer, B., Nelson, M., Lagoze, C., Sanderson, R.: ResourceSync Framework Specification – Change Notification, 2016,  \url{http://www.openarchives.org/rs/notification/1.0/notification}
  \bibitem{ref-11} Berners-Lee, T.: Cool URIs don't change, W3C, 1998,  \url{https://www.w3.org/Provider/Style/URI.html}
  \bibitem{ref-12} Archer, P., Loutas, N., Goedertier S., Kourtidis, S.: Study On Persistent URIs, 2012, \url{http://philarcher.org/diary/2013/uripersistence/}
  \bibitem{ref-13} Fielding, R. T.: Architectural Styles and the Design of Network-based Software Architectures. Doctoral dissertation, University of California, Irvine, 2000,  \url{http://www.ics.uci.edu/~fielding/pubs/dissertation/rest_arch_style.htm}
  \bibitem{ref-14} Page, K.R., De Roure, D.C., Martinez, K.: REST and Linked Data: a match made for domain driven development?, WWW, WS-REST, 2011,  \url{http://ws-rest.org/2011/proc/a5-page.pdf}
  \bibitem{ref-15} Knublauch, H., Kontokostas, D.: Shapes Constraint Language, W3C Working Draft, 2016
  \bibitem{ref-16} Speicher, S., Arwe, J., Malhotra, A.: Linked Data Platform, W3C Recommendation, 2015, \url{https://www.w3.org/TR/ldp/}
  \bibitem{ref-17} Capadisli, S., Guy, A., Auer S., Berners-Lee, T.: dokieli, 2016, \url{http://csarven.ca/dokieli}
  \bibitem{ref-18} Snell, J., Prodromou, E.: Activity Streams 2.0, W3C Candidate Recommendation, 2016, \url{https://www.w3.org/TR/activitystreams-core/}
  \bibitem{ref-19} Webber, C., Tallon, J.: ActivityPub, W3C Candidate Recommendation, 2016, \url{https://www.w3.org/TR/activitypub/}
  \bibitem{ref-20} Sporny, M.: JSON-LD and Why I Hate the Semantic Web, 2014, \url{http://manu.sporny.org/2014/json-ld-origins-2/}
\end{thebibliography}

>>>>

@@

    p{.065\textwidth}
    p{.075\textwidth}
    p{.1\textwidth}

@@

    p{.04\textwidth}

@@

                                                Web-\newline mention&

@@

                                                Resource-\newline Sync&

@@

\begin{thebibliography}{99}
  \bibitem{ref-1} Mansour, E., Sambra, A., Hawke, S., Zereba, M., Capadisli, S., Ghanem, A., Aboulnaga, A., Berners-Lee, T.: A Demonstration of the Solid Platform for Social Web Applications, WWW, Demo, 2016%, \url{http://www2016.net/proceedings/companion/p223.pdf}
  \bibitem{ref-2} Tramp, S., Frischmuth, P., Ermilov, T., Shekarpour, S., Auer, S.: An Architecture of a Distributed Semantic Social Network, Semantic Web Journal, 2012
  \bibitem{ref-3} Arndt, N., Junghanns, K., Meissner, R., Frischmuth, F., Radtke, N., Frommhold, M., Martin, M.: Structured Feedback, WWW, LDOW, 2016%, \url{http://events.linkeddata.org/ldow2016/papers/LDOW2016_paper_02.pdf}
  \bibitem{ref-4} Capadisli, S., Guy, A.: Linked Data Notifications, W3C Candidate Recommendation, 2016, \url{https://www.w3.org/TR/ldn/}
  \bibitem{ref-5} Parecki, A.: Webmention, W3C Proposed Recommendation, 2016,  \url{https://www.w3.org/TR/webmention/}
  \bibitem{ref-6} Langridge, S., Hickson, I.: Pingback 1.0, 2002,  \url{http://www.hixie.ch/specs/pingback/pingback}
  \bibitem{ref-7} Klyne, G., Groth, P.: PROV-AQ: Provenance Access and Query,  W3C Note, 2013, \url{http://www.w3.org/TR/prov-aq/}
  \bibitem{ref-8} Haslhofer, B., Popitsch, N.: DSNotify – Detecting and Fixing Broken Links in Linked Data Sets, WWW, 2010%, \url{http://eprints.cs.univie.ac.at/81/1/2010\_WWW\_DSNotify.pdf}
  \bibitem{ref-9} Passant, A., Mendes, P.N.: sparqlPuSH: Proactive notification of data updates in RDF stores using PubSubHubbub, SFSW, CEUR Workshop Proceedings, Vol. 699, 2010%, \url{http://ceur-ws.org/Vol-699/Paper6.pdf}
  \bibitem{ref-10} Klein, M., Van de Sompel, H., Warner, S., Klyne, G., Haslhofer, B., Nelson, M., Lagoze, C., Sanderson, R.: ResourceSync Framework Specification – Change Notification, 2016,  \url{http://www.openarchives.org/rs/notification/1.0/notification}
  \bibitem{ref-11} Berners-Lee, T.: Cool URIs don't change, W3C, 1998,  \url{https://www.w3.org/Provider/Style/URI.html}
  \bibitem{ref-12} Archer, P., Loutas, N., Goedertier S., Kourtidis, S.: Study On Persistent URIs, 2012, \url{http://philarcher.org/diary/2013/uripersistence/}
  \bibitem{ref-13} Fielding, R. T.: Architectural Styles and the Design of Network-based Software Architectures. Doctoral dissertation, University of California, Irvine, 2000%,  \url{http://www.ics.uci.edu/~fielding/pubs/dissertation/rest_arch_style.htm}
  \bibitem{ref-14} Page, K.R., De Roure, D.C., Martinez, K.: REST and Linked Data: a match made for domain driven development?, WWW, WS-REST, 2011%,  \url{http://ws-rest.org/2011/proc/a5-page.pdf}
  \bibitem{ref-15} Knublauch, H., Kontokostas, D.: Shapes Constraint Language, W3C Working Draft, 2016
  \bibitem{ref-16} Speicher, S., Arwe, J., Malhotra, A.: Linked Data Platform, W3C Recommendation, 2015, \url{https://www.w3.org/TR/ldp/}
  \bibitem{ref-17} Capadisli, S., Guy, A., Auer S., Berners-Lee, T.: dokieli, 2016, \url{http://csarven.ca/dokieli}
  \bibitem{ref-18} Snell, J., Prodromou, E.: Activity Streams 2.0, W3C Candidate Recommendation, 2016, \url{https://www.w3.org/TR/activitystreams-core/}
  \bibitem{ref-19} Webber, C., Tallon, J.: ActivityPub, W3C Candidate Recommendation, 2016, \url{https://www.w3.org/TR/activitypub/}
  \bibitem{ref-20} Sporny, M.: JSON-LD and Why I Hate the Semantic Web, 2014, \url{http://manu.sporny.org/2014/json-ld-origins-2/}
\end{thebibliography}
